Jane, John … Leslie? A Historical Method for Algorithmic Gender Detection

### 2014-09-17 article.Rmd
Works Cited

Landrum, in progress. Landrum, Shane. "The State's Big Family Bible: Birth Certificates, Personal Identity, and Citizenship in the United States, 1840--1950." PhD dissertation, Brandeis University, in progress.

>>>>

Landrum 2014. Landrum, Shane. "The State's Big Family Bible: Birth Certificates, Personal Identity, and Citizenship in the United States, 1840--1950." PhD dissertation, Brandeis University, August 2014.
